Functional Enrichment Tests: Intro and methods comparison

### 2023-06-22 DRAFT_Funct_Enrich.Rmd
sp blast on FE

```{r engine='bash', eval=FALSE}
cd ../blastdb
curl -O https://ftp.uniprot.org/pub/databases/uniprot/current_release/knowledgebase/complete/uniprot_sprot.fasta.gz
mv uniprot_sprot.fasta.gz uniprot_sprot_r2022_02.fasta.gz
gunzip -k uniprot_sprot_r2022_02.fasta.gz
```

@@

```{r engine='bash', eval=FALSE}
/home/shared/ncbi-blast-2.11.0+/bin/makeblastdb \
-in ../blastdb/uniprot_sprot_r2022_02.fasta \
-dbtype prot \
-out ../blastdb/uniprot_sprot_r2022_02
```

@@

No single file seems obvious or simple with respect to the primary fasta header labelled with LOCXXXXXXXXXX. Have decided to use

```
>lcl|NC_035780.1_ncrna_XR_002636969.1_1 [gene=LOC111116054] [db_xref=GeneID:111116054] [product=uncharacterized LOC111116054] [ncRNA_class=lncRNA] [transcript_id=XR_002636969.1] [location=join(13578..13603,14237..14290,14557..14594)] [gbkey=ncRNA]
TGATATTGTTGTGTGCAGAACGTGGGTCATGCTGTCTTGTTGAAGAATACCCTCAATCCAAGGCTAGATTAATCATCTAG
CCATGATATTGATGATAGCAAGATTTGTGTTGATCCTG
```

```{r engine='bash', eval=FALSE}
cd ../data

curl -O https://ftp.ncbi.nlm.nih.gov/genomes/all/GCF/002/022/765/GCF_002022765.2_C_virginica-3.0/GCF_002022765.2_C_virginica-3.0_protein.faa.gz

gunzip -k GCF_002022765.2_C_virginica-3.0_protein.faa.gz
```

>>>>

```{r engine='bash', eval=FALSE}
cd DRAFT_Funct_Enrich/annot

curl -O https://ftp.uniprot.org/pub/databases/uniprot/current_release/knowledgebase/complete/uniprot_sprot.fasta.gz

mv uniprot_sprot.fasta.gz uniprot_sprot_r2023_02.fasta.gz
gunzip -k uniprot_sprot_r2023_02.fasta.gz
```

@@

```{r engine='bash', eval=FALSE}

/home/shared/ncbi-blast-2.11.0+/bin/makeblastdb \
-in DRAFT_Funct_Enrich/annot/uniprot_sprot_r2023_02.fasta \
-dbtype prot \
-out DRAFT_Funct_Enrich/annot/uniprot_sprot_r2023_02
```

@@

The following fasta was selected for annotation: `GCF_002022765.2_C_virginica-3.0_translated_cds.faa.gz`

```{r engine='bash', eval=FALSE}
cd DRAFT_Funct_Enrich/annot

curl -O https://ftp.ncbi.nlm.nih.gov/genomes/all/GCF/002/022/765/GCF_002022765.2_C_virginica-3.0/GCF_002022765.2_C_virginica-3.0_translated_cds.faa.gz

gunzip -k GCF_002022765.2_C_virginica-3.0_translated_cds.faa.gz
```

```{r engine='bash', eval=FALSE}

head DRAFT_Funct_Enrich/annot/GCF_002022765.2_C_virginica-3.0_translated_cds.faa

```{bash}
/home/shared/ncbi-blast-2.11.0+/bin/blastp \
-query DRAFT_Funct_Enrich/annot/GCF_002022765.2_C_virginica-3.0_translated_cds.faa \
-db DRAFT_Funct_Enrich/annot/uniprot_sprot_r2023_02 \
-out DRAFT_Funct_Enrich/annot/Cvir_transcds-uniprot_blastp.tab \
-evalue 1E-20 \
-num_threads 40 \
-max_target_seqs 1 \
-outfmt 6
```
